An agent-based model of local food systems

### 2016-05-13 draft.tex
update

\documentclass[11pt, oneside]{article}
\usepackage[margin=1in]{geometry}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{graphicx}
  \graphicspath{ {images/} }
\usepackage[backend=biber,
  style=apa,
  doi=false, isbn=false, eprint=false,
  maxbibnames=10,
  maxcitenames=3,
  language=american]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{SOC901.bib}
\AtEveryBibitem{\clearfield{month}}
\AtEveryBibitem{\clearfield{day}}

@@

\subsection{Issues}

>>>>

\documentclass[11pt, oneside]{article}
\usepackage[margin=1in]{geometry}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{graphicx}
  \graphicspath{ {images/} }
\usepackage[backend=biber,
  style=apa,
  doi=false, isbn=false, eprint=false,
  maxbibnames=10,
  maxcitenames=3,
  language=american]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{LFABM.bib}
\AtEveryBibitem{\clearfield{month}}
\AtEveryBibitem{\clearfield{day}}

@@

\subsection{Issues}
As mentioned throughout the paper, data fitting and calibration remain to be the technical challenge. Whenever adding another variable or adjusting the existing interaction, the delicate balance will likely be disrupted, requiring further calibration. To facilitate the process, we are interested in machine learning and hope to implement its technique in the near future. The poor choices of functional form must be addressed if the model will ever be able to truly generate the empirical phenomena. In addition to the final performance metrics, each of the key intermediate outputs (e.g. prices, space, and time) should provide useful information. Moving toward community development, which is closely associated with local food systems, it seems unavoidable to work on social welfare functions. Apart from the technicality, a next step is to model concrete arrangements such as farmers' market and CSA based upon the current model, as well as institutions such as non-profit and government. Once we introduce those specificities, it should be ready to implement exogenous shocks such as weather, ethical misconduct, and subsidies. Finally, since it is still in the stage of crude mathematical modeling, we have hardly paid attention to the nuances and subtleties associated with the key concepts, e.g. trust, authenticity, and social embeddedness. Given the exciting pile of work ahead of us, we hope to work together with those who are in different disciplines.
